---
title: "How to Make a Proceedings Paper Submission"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: > 
    \author{{\large \bf Morton Ann Gernsbacher (MAG@Macc.Wisc.Edu)} \\ Department of Psychology, 1202 W. Johnson Street \\ Madison, WI 53706 USA
    \AND {\large \bf Sharon J.~Derry (SDJ@Macc.Wisc.Edu)} \\ Department of Educational Psychology, 1025 W. Johnson Street \\ Madison, WI 53706 USA}

abstract: >
    Include no author information in the initial submission, to facilitate
    blind review.  The abstract should be one paragraph, indented 1/8 inch on both sides,
    in 9~point font with single spacing. The heading 'Abstract'
    should be 10~point, bold, centered, with one line of space below
    it. This one-paragraph abstract section is required only for standard
    six page proceedings papers. Following the abstract should be a blank
    line, followed by the header 'Keywords' and a list of
    descriptive keywords separated by semicolons, all in 9~point font, as
    shown below.
    
keywords: >
    Add your choice of indexing terms or keywords; kindly use a semi-colon; between each term.
    
output: cogsci2016::cogsci_paper
#final-submission: \cogscifinalcopy
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, 
                      fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, 
                      message=F, sanitize = T)
```

# Introduction
What do children tend to see in their everyday lives? While an understanding of children's visual enviornment is central to both theories of language acquisition and visual development, we know remarkably little about the categories and objects that tend to be in the infant view, or how they experience. For example, how often do infants tend to see animals in real-life vs. in storybooks or as toys? How consistent are the broad characteristic of children's visual environemtn across children, and across developmental time?

To answer these questions, over the past decade, researchers have started to document the infant egocentric perspective using head-mounted cameras [@yoshida2008;@franchak2011],quantifying the degree to which there are substantial shifts in their viewpoints that may have downstream developmental consequences.  
Indeed; as adults it is hard to intuit how strange this viewpoint can be, and how much it varies across development, transitioning over the first two years of life from close-up views of faces to restricted views of hands manipulating objects [@fausey2016; @long2020detecting] with children's postural developments shaping what they see [sanchez2018].
Most work, however, has focused on documenting the social information that infants and children have access to across early development  [@yoshida2008; @sanchez2018; @fausey2016]. 

More recent reseach has made progress towards understanding the object  object categories that infants see, starting with  annotating the basic-level categories (e.g., spoons, cups) in the view of 8-month-olds during mealtime. This research has revealed tantalizing findings--suggesting that a small number of objects are both pervasively present and among infants' first-learned words [@clerkin2017], and that, more broadly the objects in the infant view tend to have a Zipfian distribution -- as do the words in child-directed speech (CITE). These findings suggest that an understanding of visual enviornment of infants and young children could yield insights about early category and language learning.

Here, we take a step towards characterizing the visual enviornment of young children by analyzing the categories of objects (e.g., animals, vehicles, toys, people) present in the infant view in a longtiudinal corpus of head-mounted camera data [@sullivan2020]. We choose to annotate these categories (rather than the basic-level identities of objects) in order to have broader coverage over a large sample of frames and developmental time, and because the basic-level identities of many objects --  especially certain toys or objects viewed from odd angles -- are sometimes ambigous (and therefore would be inconsistent across annotators).  We thus collected human annotations of a large, randomly sampled set of frames (24,000 frames) from two children in the longitudinal dataset, allowing the analysis of the proportion of broad categories in the infant view from 6-32 months of age.

Using these annotations, we conducted three sets of analyses. First, we explored the prevalence of each of the broad categories that were annotated across developmental time (and across children). Prior work documenting the proportion of faces/hands in view has suggested some developmental change in how children view the world across this same age range--and in this same dataset [@long2020]. On this account,  categories that children are liekly to interact with (i.e., toys, small objects) may become more prevalent in the child's view across age, whereas other, more stable cateogries (i.e., furniture) would show relative consistency. On the other hand, the broad characteristics children's visual environments may be relatively stable and determined mostly by the activities that they tend to engage in.  Second, we examined whether the proportion of animals vs. inanimate objects would be relatively equal. A long literature has documented that even newborns have a tendency to attend to animate agents [@farroni2005] (CITES),  animal words tend to be amoung children's first-learned words, and visual cortex dedicates a remarkable amount of space to making fine-grained distinctions amoung different animals [@konkle2013] (CITES). Howver, at present, it is unknown whether (non-human) animates (e.g., cats, dogs, other animals) are prevalent in the infant viewpoint, and whether they tend to be exemplars of real-life animals (e.g., ducks at a park) or mostly illustrations in storybooks or as toy stuffed animals. Finally, while some activity contexts  (e.g., storytime) and lead to intuitive co-occurances between object cateogries (e.g., books and people), we conducted a set of data-driven, exploratory analyses examinig the co-occurance of all broad categories to identify other, reliable patterns in how infants experience their visual world.


# Set up libraries
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rjson)
library(here)
library(lubridate)
library(magick)
library(ggthemes)
```

# Load preprocessed data
```{r}
load(file = here::here('data/preprocessed_data/goldset_category_annotations.RData'))
```

## Frequency of each category by age
```{r}
freq_by_categories_by_age <- d %>%
  group_by(age_day_bin) %>%
  mutate(count_frames = n())  %>%
  ungroup() %>%
  group_by(category, age_day_bin, child_id) %>%
  dplyr::summarize(count_categories = n(), count_frames = count_frames[1]) %>%
  mutate(freq = count_categories / count_frames)

```

# Acknowledgements

Place acknowledgments (including funding information) in a section at
the end of the paper.

# References 

```{r}
# References will be generated automatically by Pandoc and included here.
# The following code is some latex to format the bibliography. Do not remove it.
```

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}
\noindent
