---
title: "How to Make a Proceedings Paper Submission"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: > 
    \author{{\large \bf Morton Ann Gernsbacher (MAG@Macc.Wisc.Edu)} \\ Department of Psychology, 1202 W. Johnson Street \\ Madison, WI 53706 USA
    \AND {\large \bf Sharon J.~Derry (SDJ@Macc.Wisc.Edu)} \\ Department of Educational Psychology, 1025 W. Johnson Street \\ Madison, WI 53706 USA}

abstract: >
    Include no author information in the initial submission, to facilitate
    blind review.  The abstract should be one paragraph, indented 1/8 inch on both sides,
    in 9~point font with single spacing. The heading 'Abstract'
    should be 10~point, bold, centered, with one line of space below
    it. This one-paragraph abstract section is required only for standard
    six page proceedings papers. Following the abstract should be a blank
    line, followed by the header 'Keywords' and a list of
    descriptive keywords separated by semicolons, all in 9~point font, as
    shown below.
    
keywords: >
    Add your choice of indexing terms or keywords; kindly use a semi-colon; between each term.
    
output: cogsci2016::cogsci_paper
#final-submission: \cogscifinalcopy
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, 
                      fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, 
                      message=F, sanitize = T)
```

# Introduction
What do children tend to see in their everyday lives? Beneath this simple question lies a host of questions central to both theories of early word learning and visual development. Children must make an impressive visual generalization to learn that the word ``dog'' refers to a category \textit{dog} that includes golden retrievers and Chihuahuas, but does not include cows or other four-legged animals \citep{markman1990}. Tet we know remarkably little about the everyday inputs for this generalization. For example, how often do infants tend to see \textit{dogs} in real-life vs. in storybooks? 

To answer these questions, over the past decade, researchers have started to document the infant egocentric perspective using head-mounted cameras \citep{yoshida2008,franchak2011},quantifying the degree to which there are substantial shifts in their viewpoints that may have downstream developmental consequences.  
Indeed, as adults it is hard to intuit how strange this viewpoint can be, and how much it varies across development, transitioning over the first two years of life from close-up views of faces to restricted views of hands manipulating objects \citep{fausey2016, } with children's postural developments shaping what they see \citep{sanchez2018}.
Most work, however, has focused on documenting the social information that infants and children have access to across early development  \citep{yoshida2008, sanchez2018, fausey2016}.
Recent research has started to link what infants see with the words they learn, finding that a small number of objects are both pervasively present during mealtime for 8-10 month-olds (e.g., spoons, cups) and among infants' first-learned words \citep{clerkin2017}, and that the objects in the infant view tend to have a Zipfian distribution -- as do the words in child-directed speech (CITE).
These findings suggest that an understanding of visual enviornment of infants and young children could yield insights about early category and language learning. 


<!-- And changes in social info with posture -->
More focus on toys vs. faces during playt
ime Franchak)

Here, we examine the broad statistics of what children tend to see in their everyday lives, taking data from SAYcam
Describe the dataset a bit
Describe why we choose these broad categories
Describe the random sampling across age 

What we could find
How much of a kid’s world is the “kid-relevant” stuff vs. everything else?
Kid-relevant stuff comes to mind when we think of kids. But many studies have shown that sometimes our intuition is wrong about the child-directed view… 
Relative prevalence of animals vs. objects
LARGE portion of cortex likes animals, and a lot of studies show heightened attention to animals (relative to objects); 
Might expect equal proportion of attention to animals vs. to objects when they are present
Developmental change of prevalence rates 
Social signal work / posture work -- suggests we might see some change over age in toys/small objects 
On the other hand, kid’s environment might be rather stable and dictated by their parents/routines
On the other hand, intuition says maybe not


# Set up libraries
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rjson)
library(here)
library(lubridate)
library(magick)
library(ggthemes)
```

# Load preprocessed data
```{r}
load(file = here::here('data/preprocessed_data/goldset_category_annotations.RData'))
```



# Acknowledgements

Place acknowledgments (including funding information) in a section at
the end of the paper.

# References 

```{r}
# References will be generated automatically by Pandoc and included here.
# The following code is some latex to format the bibliography. Do not remove it.
```

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}
\noindent
