---
title: "SAYCAM-objects"
author: "Bria Long"
date: "12/18/2020"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rjson)
library(here)
library(lubridate)
library(magick)
library(ggthemes)
```

# Import data
## Filename to import data from sagemaker
```{r}
filename = here::here('data/saycam_goldset_annotations/24k/output.manifest')
```

## Use this awk construction to read the nested json
```{r}
json = fromJSON(paste("[",paste(readLines(filename),collapse=","),"]"))
```

## Create readable class list -- double checked via turk interface and data structure
```{r}
class_list = c('Animal-toy','Animal-real', 'Vehicle-toy','Vehicle-real','Toy','Utensil-Dish','Food','Furniture','Book','Person','Clothing','Plant', 'SmallObj','BigObj','Other','Nothing')

d <- tibble() 
```

## Go through each row and extract data we want; ignoring conf
```{r}
for (i in 1:24000){
  this_image = json[[i]]
  source_url = this_image$`source-ref`
  classes_in_image = this_image$`SAYCAM-classification-goldset-24k`
  classes_in_image = classes_in_image + 1
  these_confs =unlist(this_image$`SAYCAM-classification-goldset-24k-metadata`$`confidence-map`)
  categories_in_image = class_list[classes_in_image]
  new_rows = tibble(img = source_url, class = classes_in_image, category = categories_in_image, conf = these_confs)
  
  d <- d %>% 
    bind_rows(new_rows)
    
}

```


# Add age data
## Birthdays
```{r}
bday_s_approx = lubridate::ymd(20121017)
bday_a_approx = lubridate::ymd(20120913)
bday_y_approx = lubridate::ymd(20180214)

bday = c(bday_s_approx,bday_a_approx, bday_y_approx)
child_id  = c('S','A','Y')
age_info = tibble(bday,child_id)

```

## get public url
```{r}
prefix = 'https://langcog.stanford.edu/expts/saycam/frames/'
d <- d %>%
  mutate(img_name = str_split_fixed(img,'/',5)[,5]) %>%
  mutate(public_url = paste0(prefix,img_name))
```

## break out vid name / date filmed / age days
```{r} 
d <- d %>%
  mutate(vid_name_temp = str_split_fixed(img_name,'-',2)[,2]) %>%
  mutate(vid_name = str_split_fixed(vid_name_temp, '.mp4',2)[,1])  %>%
  mutate(child_id = str_split_fixed(vid_name, '_',2)[,1]) %>%
  mutate(date_filmed =  lubridate::ymd(str_split_fixed(vid_name, '_',4)[,2])) %>%
  left_join(age_info) %>%
  mutate(age_days = as.numeric(difftime(date_filmed,bday)) ) %>%
  select(-bday, -date_filmed)
```

## construct age bins for every month 
```{r}
bin_size = 30 # days
min_age = min(d$age_days, na.rm=TRUE)
max_age = max(d$age_days, na.rm=TRUE)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)

d <- d %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) 
```


```{r}
d <- d %>%
  filter(conf > quantile(conf,.25))
```

# save out datafile
```{r}
dir.create(here::here('data/preprocessed_data/'))
save(file = here::here('data/preprocessed_data/goldset_category_annotations.RData'), d)
```

