---
title: "SAYCAM-objects"
author: "Bria Long"
date: "12/18/2020"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rjson)
library(here)
library(lubridate)
library(magick)
library(ggthemes)
```

# Filename to import data from sagemaker
```{r}
filename = here::here('data/saycam_goldset_annotations/24k/output.manifest')
```

### Use this awk construction to read the nested json
```{r}
json = fromJSON(paste("[",paste(readLines(filename),collapse=","),"]"))
```

### Create readable class list -- double checked via turk interface and data structure
```{r}
class_list = c('Animal-toy','Animal-real', 'Vehicle-toy','Vehicle-real','Toy','Utensil-Dish','Food','Furniture','Book','Person','Clothing','Plant', 'SmallObj','BigObj','Other','Nothing')

d <- tibble() 
```

### Go through each row and extract data we want; ignoring conf
```{r}
for (i in 1:24000){
  this_image = json[[i]]
  source_url = this_image$`source-ref`
  classes_in_image = this_image$`SAYCAM-classification-goldset-24k`
  classes_in_image = classes_in_image + 1
  these_confs =unlist(this_image$`SAYCAM-classification-goldset-24k-metadata`$`confidence-map`)
  categories_in_image = class_list[classes_in_image]
  new_rows = tibble(img = source_url, class = classes_in_image, category = categories_in_image, conf = these_confs)
  
  d <- d %>% 
    bind_rows(new_rows)
    
}
```


## Add age data


```{r}
bday_s_approx = lubridate::ymd(20121017)
bday_a_approx = lubridate::ymd(20120913)
bday_y_approx = lubridate::ymd(20180214)

bday = c(bday_s_approx,bday_a_approx, bday_y_approx)
child_id  = c('S','A','Y')
age_info = tibble(bday,child_id)

```


```{r}
d <- d %>%
  mutate(img_name = str_split_fixed(img,'/',5)[,5]) %>%
  mutate(public_url = paste0(prefix,img_name))
```

```{r} 
d <- d %>%
  mutate(vid_name_temp = str_split_fixed(img_name,'-',2)[,2]) %>%
  mutate(vid_name = str_split_fixed(vid_name_temp, '.mp4',2)[,1])  %>%
  mutate(child_id = str_split_fixed(vid_name, '_',2)[,1]) %>%
  mutate(date_filmed =  lubridate::ymd(str_split_fixed(vid_name, '_',4)[,2])) %>%
  left_join(age_info) %>%
  mutate(age_days = as.numeric(difftime(date_filmed,bday)) ) %>%
  select(-bday, -date_filmed)
```

# Age bins
```{r}
bin_size = 30 # days
min_age = min(d$age_days, na.rm=TRUE)
max_age = max(d$age_days, na.rm=TRUE)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)

d <- d %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) 
```


# Graph basic descriptives
```{r}
freq <- d %>%
  group_by(category) %>%
  dplyr::summarize(count = n()) %>%
  mutate(freq = count / sum(count)) %>%
  arrange(desc(freq)) %>%
  mutate(category = fct_reorder(category, count, .desc=TRUE))
```

```{r}
ggplot(data=freq, aes(x=category, y=freq)) +
  geom_point() +
  theme_few() +
  ylab('Proportion frames detected') +
  xlab('Category') + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

```
# category by age
```{r}



freq_by_categories_by_age <- d %>%
  group_by(age_day_bin) %>%
  mutate(count_frames = n())  %>%
  ungroup() %>%
  group_by(category, age_day_bin, child_id) %>%
  dplyr::summarize(count_categories = n(), count_frames = count_frames[1]) %>%
  mutate(freq = count_categories / count_frames)

```

```{r}
ggplot(data=freq_by_categories_by_age, aes(x=age_day_bin, y=freq, size=count_frames, col=child_id)) +
  theme_few() + 
  geom_point(alpha=.8) +
  geom_smooth(span=20, aes(weight=count_frames)) +
  facet_wrap(~category) +
  xlab('Age (months)') +
  ylab('Proportion frames detected')

```

```{r}
frames_with_things <- d %>%
  filter(!category %in% c('Nothing')) %>%
  group_by(img) %>%
  summarize(count_dets = n())

```

### Add url so we can make montages
```{r}
prefix = 'http://langcog.stanford.edu/expts/saycam/frames/'

```

# Data visualizations
## Make montages for visualizations

```{r}
dir.create(here::here('data/example-montages/'))

for (c in class_list) {
  this_class <- d %>%
    filter(category == c) %>%
    filter(conf>.8) %>%d
    dplyr::sample_n(10)

  image_read(this_class$public_url) %>%
    image_append(stack = FALSE) %>%
    image_write(paste0(here::here("data/example-montages/"), c,".png"))
}
```

## Look at conjunction analyses
```{r}
play <- d %>%
  filter(category=='Person' | category=='Toy') %>%
  group_by(img, public_url) %>%
  dplyr::summarize(play_frame = n()) %>%
  filter(play_frame>1) %>%
  sample_n(10)

image_read(play$public_url) %>%
    image_append(stack = FALSE) %>%
    image_write(paste0(here::here("data/example-montages/play.png")))
```


```{r}
storytime <- d %>%
  filter(category=='Person' | category=='Book') %>%
  group_by(img, public_url) %>%
  dplyr::mutate(conjunction = n()) %>%
  filter(conjunction>1) %>%
  ungroup() %>%
  dplyr::sample_n(10)


image_read(storytime$public_url) %>%
    image_append(stack = FALSE) %>%
    image_write(paste0(here::here("data/example-montages/storytime.png")))
```


```{r}
storytime_by_age <-  d %>%
  group_by(age_day_bin) %>%
  mutate(count_frames_by_bin = n()) %>%
  filter(category=='Person' | category=='Book') %>%
  group_by(img) %>%
  mutate(conjunction = n()) %>%
  filter(conjunction>1) %>%
  group_by(age_day_bin) %>%
  mutate(freq = n()/count_frames_by_bin)

ggplot(data=storytime_by_age, aes(x=age_day_bin, y=freq)) +
  geom_point() +
  geom_smooth(span=10)
```


# Get long form data to look at conjunctions
```{r}
d_by_image <-  d %>%
  select(public_url, age_days, age_day_bin, child_id, category, conf) %>%
  spread(key = category, value=conf) 

d_by_image <- d_by_image %>%
  mutate(book_person = (Book>0) & (Person>0)) %>%
  mutate(toy_person = is.na(Book) & (Person>0) & (Toy>0)) %>%
  mutate(toy_person = is.na(Book) & (Person>0) & (Toy>0)) %>%
  mutate(animal_all = (`Animal-real`>0) | (`Animal-toy`>0)) %>%
  mutate(big_obj = (BigObj>0) | (Furniture>0) | (`Vehicle-real`>0)) %>%
  mutate(small_obj = (SmallObj>0) | (Toy>0) | (`Utensil-Dish`>0) | (Food>0))


```

```{r}
animacy_size <- d_by_image %>%
  group_by(age_day_bin, child_id) %>%
  dplyr::summarize(count_anim = sum(animal_all, na.rm=TRUE), count_big = sum(big_obj, na.rm=TRUE), count_small = sum(small_obj, na.rm=TRUE), count_frames = n(), count_people = sum(Person>0, na.rm=TRUE)) %>%
  mutate(Animals = count_anim / count_frames, BigObj = count_big / count_frames, People = count_people / count_frames, SmallObj = count_small / count_frames) %>%
  gather(key = anim_size, value = freq, BigObj, People, SmallObj, Animals) %>%
  select(-count_anim, -count_big, -count_small)

```

```{r}
ggplot(data=animacy_size, aes(x=age_day_bin, y=freq, col=anim_size, size=count_frames)) +
  geom_point(alpha=.5) +
  theme_few() +
  geom_smooth(span=10) + 
  xlab('Age (in months)') +
  ylab('Proportion detected')

```


```{r}
freq_by_categories_by_age <- d %>%
  group_by(img) %>%
  mutate(count_frames = n())  %>%
  ungroup() %>%
  group_by(category, age_day_bin, child_id) %>%
  dplyr::summarize(count_categories = n(), count_frames = count_frames[1]) %>%
  mutate(freq = count_categories / count_frames)
```

```{r}
short_form <- d %>%
  select(img, category) %>%
  xtabs(~ID + Country, data = ., sparse = FALSE)

ggcorr(matrix, method = c("everything", "pearson")) 

```

